### 2020-05-21 ArticleAcortado.tex
Menuda mierda colega

A relevant aspect of this result is that the limit probability of any FO
property in $G(n,p(n))$ when $p(n)\sim \beta/n$ varies analytically with $\beta$.
A consequence of this is that in this conditions no FO property can "capture" sudden changes 
in the structure of $G(n,p(n))$. \par
It was left open at the end of \cite{lynch1992probabilities} whether the convergence law obeyed
by $G(n,\beta/n)$ could be generalized for other random models of relational structures
that contain relations of degree greater than $2$.
A result in this regard was obtained in \cite{salvadorbrasil}, 
among other zero-one and convergence laws.
There it is considered $G^d(n,p)$ the random model of $d$-uniform hypergraphs where
each $d$-edge is added to a set of $n$ labeled vertices with probability $p$ independently.
It is shown that when $p(n)\sim \beta/n^{d-1}$ -i.e., when the expected number of
edges is linear- then $G^d(n,p(n))$ obeys a convergence law with respect of the FO
language of $d$-uniform hypergraphs. With little additional work it can be shown that
in this conditions the limit probability of any FO property of $G^d(n,p(n))$ varies 
analytically with $\beta$. \par
We aim to extend this last result to arbitrary relational structures
to whose relations we can impose symmetry and anti-reflexivity constraints. 
This generalization is motivated by an application to the problem of random 
satisfiability. We continue the study started by Atserias in \cite{atserias2005definability}
with regards to the definability in first order logic of certificates for unsatisfiability
that hold for typical unsatisfiable formulas. There it is considered a random model for
$3$-CNF formulas where each possible clause over $n$ variables is added with probability $p$ 
independently. This way the expected number of clauses is $\Theta(n^3p)$ as $n$ grows.
The main result of that article states that when the expected number of clauses is $\Theta(n^{2+\alpha})$
for any arbitrary $\alpha>0$ then there exists some FO property of $3$-CNF formulas that implies
unsatisfiability and asymptotically almost surely (a.a.s) holds for unsatisfiable formulas. 
Furthermore, if the expected number of clauses is $\Theta(n^{2-\alpha})$ for any irrational
$\alpha>0$ then no FO property that implies unsatisfiability holds a.a.s
for unsatisfiable formulas.

@@

\begin{theorem} \label{thm:BigTrees}
	Fix $r\in \N$. The following are satisfied:
	\begin{itemize}
		\item[(1)] Let $\mathbf{T}$ be a
		$k$-equivalence class for trees with radii at most $r$.	Then 
		$
		\mathrm{Pr}[r,\mathbf{T}]
		$
		exists,
		is positive for all choices of 
		$\{\beta_R\}_{R\in \epsilon}\in (0,\infty)^{|\sigma|}$,
		and is an expression
		in $\Lambda$.
		\item[(2)] Let $\overline{u}\in (\N)_*$,
		and let $\pi(\overline{x})\in FO[\sigma]$ be a consistent
		edge sentence such that 
		$len(\overline{x})=len(\overline{u})$.
		Let $\overline{v}\in (\N)_*$ be vertices contained
		in $\overline{u}$. For each $v\in \overline{v}$
		let $\mathbf{T}_v$ be a $k$-equivalence class
		of trees with radii	at most $r$. Then
		\[
		\Ln \mathrm{Pr}\left( \bigwedge_{v\in \overline{v}} 
		Tr\left(G_n, \overline{u};\,\,v;\,\,r\right)\in \mathbf{T}_v 
		\, | \, \pi(\overline{u})
		\right)= \prod_{v\in \overline{v}} \mathrm{Pr}[r,\mathbf{T}_v]. \]	 	
	\end{itemize}
\end{theorem}
We will devote the rest of this section to proving this
theorem. The proof will be done by induction on $r$. 
Recall that	all trees with radius zero are $k$-equivalent. Thus,
the limits appearing in conditions (1) and (2) are both equal to $1$
in the case $r=0$. In consequence we obtain the following.

@@

\section*{Conclusions}

>>>>

A relevant aspect of this result is that the limit probability of any FO
property in $G(n,p(n))$ when $p(n)\sim \beta/n$ varies analytically with $\beta$.
A consequence of this is that in this conditions no FO property can "capture" sudden changes 
in the structure of $G(n,p(n))$. \par
It was left open at the end of \cite{lynch1992probabilities} whether the convergence law obeyed
by $G(n,p(n))$in the range $p(n)\sim \beta/n$
could be generalized for other random models of relational structures 
that contain relations of degree greater than $2$.
A result in this regard was obtained in \cite{salvadorbrasil}, 
among other zero-one and convergence laws.
There it is considered $G^d(n,p)$ the random model of $d$-uniform hypergraphs where
each $d$-edge is added to a set of $n$ labeled vertices with probability $p$ independently.
It is shown that when $p(n)\sim \beta/n^{d-1}$ -i.e., when the expected number of
edges is linear- then $G^d(n,p(n))$ obeys a convergence law with respect of the FO
language of $d$-uniform hypergraphs. With little additional work it can be shown that
in this conditions the limit probability of any FO property of $G^d(n,p(n))$ varies 
analytically with $\beta$. We 
extend this result to arbitrary relational structures
to whose relations we can impose symmetry and anti-reflexivity constraints 
(\cref{thm:main}). \par

This generalization is motivated by an application to the problem of random 
satisfiability. We continue the study started by Atserias in \cite{atserias2005definability}
with regards to the definability in first order logic of certificates for unsatisfiability
that hold for typical unsatisfiable formulas. There it is considered a random model for
$3$-CNF formulas where each possible clause over $n$ variables is added with probability $p$ 
independently. This way the expected number of clauses is $\Theta(n^3p)$ as $n$ grows.
The main result of that article states that when the expected number of clauses is
$\Theta(n^{2+\alpha})$ for any arbitrary $\alpha>0$ then there exists some 
FO property of $3$-CNF formulas that implies
unsatisfiability and asymptotically almost surely (a.a.s) holds for unsatisfiable formulas. 
Furthermore, if the expected number of clauses is $\Theta(n^{2-\alpha})$ for any irrational
$\alpha>0$ then no FO property that implies unsatisfiability holds a.a.s
for unsatisfiable formulas. We complement this result by showing that 
in a random $l$-CNF formula were each clause over $n$ variables is chosen  
with probability $p(n)$ independently when the expected number of clauses is 
$\Theta(n)$ there is no FO property that certifies unsatisfiability and
holds a.a.s for unsatisfiable formulas (\cref{thm:mainsat}).

@@

\begin{theorem} \label{thm:BigTrees}
	Fix $r\in \N$. The following are satisfied:
	\begin{itemize}
		\item[(1)] Let $\mathbf{T}$ be a
		$k$-equivalence class for trees with radii at most $r$.	Then 
		$
		\mathrm{Pr}[r,\mathbf{T}]
		$
		exists,
		is positive for all choices of 
		$\{\beta_R\}_{R}\in (0,\infty)^{|\sigma|}$,
		and is an expression
		in $\Lambda$.
		\item[(2)] Let $\overline{u}\in (\N)_*$,
		and let $\pi(\overline{x})\in FO[\sigma]$ be a consistent
		edge sentence such that 
		$len(\overline{x})=len(\overline{u})$.
		Let $\overline{v}\in (\N)_*$ be vertices contained
		in $\overline{u}$. For each $v\in \overline{v}$
		let $\mathbf{T}_v$ be a $k$-equivalence class
		of trees with radii	at most $r$. Then
		\[
		\Ln \mathrm{Pr}\left( \bigwedge_{v\in \overline{v}} 
		Tr\left(G_n, \overline{u};\,\,v;\,\,r\right)\in \mathbf{T}_v 
		\, | \, \pi(\overline{u})
		\right)= \prod_{v\in \overline{v}} \mathrm{Pr}[r,\mathbf{T}_v]. \]	 	
	\end{itemize}
\end{theorem}
We will devote the rest of this section to proving this
theorem. The proof will be done by induction on $r$. 
Recall that	all trees with radius zero are $k$-equivalent. Thus,
the limits appearing in conditions (1) and (2) are both equal to $1$
in the case $r=0$. In consequence we obtain the following.

@@
